---
title: "Hw6"
author: "Jiayan"
date: "4/6/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We seperate the data by date, and pick the stock prices.
```{r echo=FALSE}
library(readxl)
goog <- read_excel("/Users/yynpy/Desktop/courses/FIN567 financial risk management/hw/hw6/F567C.s2018.HW6.GOOG data.xlsx")
goog <- goog[-c(1,2,3,4),]
```

```{r seperate}
d1 <- subset(goog,X__1=='41311')
d2 <- subset(goog,X__1=='41312')
d3 <- subset(goog,X__1=='41313')
d4 <- subset(goog,X__1=='41316')
d5 <- subset(goog,X__1=='41317')
d6 <- subset(goog,X__1=='41318')
d7 <- subset(goog,X__1=='41319')
d8 <- subset(goog,X__1=='41320')
d9 <- subset(goog,X__1=='41324')
d10 <- subset(goog,X__1=='41325')
s <- list()
s[[1]] <- as.numeric(d1$X__7)
s[[2]] <- as.numeric(d2$X__7)
s[[3]] <- as.numeric(d3$X__7)
s[[4]] <- as.numeric(d4$X__7)
s[[5]] <- as.numeric(d5$X__7)
s[[6]] <- as.numeric(d6$X__7)
s[[7]] <- as.numeric(d7$X__7)
s[[8]] <- as.numeric(d8$X__7)
s[[9]] <- as.numeric(d9$X__7)
s[[10]] <- as.numeric(d10$X__7)
```

Realizedd variance is estimated by self-defined function rv.
```{r rvfunction}
rv <- function(price,interval){
  r <- NULL
  for (i in 1:length(price) - interval){
    r[i] <- log(price[i + interval]/price[i])
  } 
  sum <- sum((na.omit(r))^2/interval)
  return(sum)
}
```

## 1
```{r Q1}
rv.q1 <- NULL
for (i in 1:10){
  rv.q1[i] <- rv(s[[i]],1)
}
print(rv.q1)
mean(rv.q1)
```
## 2
(a)
(c)
The variance estimates decrease as the return interval increases. The ratio of the average (across days) average realized variance based on 15-minute returns to the average (across days) realized variance based on 1-minute returns is 0.0000687/ 0.0000881
= 0.7800597. The ratio of the average (across days) average realized variance based on 15- minute returns to the average (across days) average realized variance based on 10-minute returns is 0.0000687/0.0000708 = 0.9701889 or just over 97%. Thus, the realized variance estimate seems to stabilize at a return interval of about 15 minutes.

## 3

## 4
